---
title: "Adj DK Pts with Course Fit Sim"
author: "Jarrod Pelkofer"
date: "3/31/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Libraries
```{r}
library(plotly)
library(DataExplorer)

source(file = "simulation_scripts/adj_dk_course_fit_sim_script.R")

plan(multisession, workers = 4)

theme_set(theme_minimal())

dk_past_results <- 
  read_csv("dk_past_results.csv") %>% 
  janitor::clean_names() %>% 
  mutate(date = mdy(date)) %>% 
  filter(date %>% between(left = ymd("2019-01-13"), right = ymd("2019-08-25")))
```

# Remove Tournaments - that are non-cut events or three-day cut event
```{r}
dk_past_results <- 
  dk_past_results %>% 
  filter(!tournament_id %in% c(401056511, 401056514, 401056516, 401056542, 401056559, 401056543 ))
```

# Pull Tournaments to Sim
```{r}
tournaments_to_sim <- 
  dk_past_results %>% 
  select(tournament_id, tournament_name, course, date) %>% 
  mutate(date = date - days(4)) %>% 
  distinct() %>% 
  separate(course, into = c("course", "location"), sep = " - ") %>% 
  mutate(course = case_when(
    course == "Spyglass Hill" ~ "Spyglass Hill GC",
    course == "Riviera" ~ "Riviera Country Club", 
    course == "Torrey Pines" ~ "Torrey Pines North", 
    course == "PGA National" ~ "PGA National Champion Course", 
    course == "Innisbrook" ~ "Innisbrook Resort -Copperhead", 
    course == "TPC San Antonio" ~ "TPC San Antonio (Oaks)",
    course == "Muirfield Village" ~ "Muirfield Village GC",
    course == "Keene Trace" ~ "Keene Trace GC", 
    course == "TPC Southwind, Memphis, TN" ~ "TPC Southwind",
    TRUE ~ course
  )) %>% 
  mutate(tournament_name = case_when(
    tournament_name == "The Memorial Tournament pres. by Nationwide" ~ "the Memorial Tournament",
    tournament_name == "WGC-FedEx St. Jude Classic" ~ "FedEx St. Jude Classic",
    tournament_name == "Arnold Palmer Invitational Pres. by Mastercard" ~ "Arnold Palmer Invitational",
    TRUE ~ tournament_name
  ))
```

# Bring in hole category data and join with tournament name
```{r}
con <- dbConnect(
  drv = RPostgres::Postgres(),
  user = "postgres",
  password = keyring::key_get("postgres_db", "postgres"),
  dbname = "golf_db",
)

tournaments_tbl <- tbl(con, "tournaments_tbl") %>% collect()

hole_categories_tbl <- 
  read_csv("cluster_holes/past_holes_categorized/hole_categories_tbl.csv") %>% 
  separate(col = tournament_round_id, into = "tournament_id", sep = "_", remove = FALSE) %>% 
  # select(tournament_id, hole_category, adj_field_dk_avg) %>% 
  left_join(select(tournaments_tbl, tournament_id, tour, season, tournament_name, course), by = "tournament_id")


```

# Hole Category Distribution Per Tournament
```{r}
hole_difficulties_per_tournament <- 
  hole_categories_tbl %>% 
  filter(tour == "pga") %>% 
  mutate(tournament_name = case_when(
    tournament_name == "2017 Masters Tournament" ~ "Masters Tournament",
    tournament_name == "2018 Masters Tournament" ~ "Masters Tournament",
    tournament_name == "SBS Tournament of Champions" ~ "Sentry Tournament of Champions",
    tournament_name == "Fort Worth Invitational" ~ "Charles Schwab Challenge",
    tournament_name == "DEAN &amp; DELUCA Invitational" ~ "Charles Schwab Challenge",
    tournament_name == "TOUR Championship" ~ "Tour Championship",
    tournament_name == "World Golf Championships-Bridgestone Invitational" ~ "WGC-Bridgestone Invitational",
    tournament_name == "Shell Houston Open" ~ "Houston Open",
    tournament_name == "AT&amp;T Pebble Beach Pro-Am" ~ "AT&T Pebble Beach Pro-Am",
    tournament_name == "AT&amp;T Byron Nelson" ~ "AT&T Byron Nelson",
    tournament_name == "THE PLAYERS Championship" ~ "The Players Championship",
    tournament_name == "CareerBuilder Challenge" ~ "Desert Classic",
    tournament_name == "Northern Trust Open" ~ "Genesis Open",
    tournament_name == "World Golf Championships-Mexico Championship" ~ "WGC-Mexico Championship",
    TRUE ~ tournament_name
  )) %>% 
  group_by(tournament_name, course, hole_category) %>% 
  summarise(total = n()) %>% 
  ungroup() %>% 
  left_join(
    hole_categories_tbl %>% 
  filter(tour == "pga") %>% 
  mutate(tournament_name = case_when(
    tournament_name == "2017 Masters Tournament" ~ "Masters Tournament",
    tournament_name == "2018 Masters Tournament" ~ "Masters Tournament",
    tournament_name == "SBS Tournament of Champions" ~ "Sentry Tournament of Champions",
    tournament_name == "Fort Worth Invitational" ~ "Charles Schwab Challenge",
    tournament_name == "DEAN &amp; DELUCA Invitational" ~ "Charles Schwab Challenge",
    tournament_name == "TOUR Championship" ~ "Tour Championship",
    tournament_name == "World Golf Championships-Bridgestone Invitational" ~ "WGC-Bridgestone Invitational",
    tournament_name == "Shell Houston Open" ~ "Houston Open",
    tournament_name == "AT&amp;T Pebble Beach Pro-Am" ~ "AT&T Pebble Beach Pro-Am",
    tournament_name == "AT&amp;T Byron Nelson" ~ "AT&T Byron Nelson",
    tournament_name == "THE PLAYERS Championship" ~ "The Players Championship",
    tournament_name == "CareerBuilder Challenge" ~ "Desert Classic",
    tournament_name == "Northern Trust Open" ~ "Genesis Open",
    tournament_name == "World Golf Championships-Mexico Championship" ~ "WGC-Mexico Championship",
    TRUE ~ tournament_name
  )) %>%
    group_by(tournament_name, course) %>% 
    summarise(total_holes = n()) %>% 
    ungroup(),
  by = c("tournament_name", "course")
  ) %>% 
  mutate(hole_distribution = total / total_holes,
         holes_per_round = round(hole_distribution * 18, 0)) %>% 
  ungroup() %>% 
  pivot_wider(id_cols = c(tournament_name, course), names_from = hole_category, values_from = holes_per_round) %>% 
  mutate(total_holes = easy + medium + hard) %>% 
  mutate(medium = case_when(
    total_holes == 19 ~ medium - 1,
    total_holes == 17 ~ medium + 1,
    TRUE ~ medium)) %>% 
  mutate(total_holes = easy + medium + hard) %>% 
  mutate(course = case_when(
    course == "Bay Hill Club &amp; Lodge" ~ "Bay Hill",
    course == "Augusta National Golf Club" ~ "Augusta National",
    course == "Harbour Town Golf Links" ~ "Harbour Town",
    course == "Quail Hollow Club" ~ "Quail Hollow",
    course == "Trinity Forest Golf Club" ~ "Trinity Forest",
    course == "Colonial CC" ~ "Colonial",
    course == "Sedgefield Country Club" ~ "Sedgefield",
    course == "East Lake Golf Club" ~ "East Lake",
    course == "Club De Golf Chapultepec" ~ "Chapultepec",
    TRUE ~ course
  ))
  
```

# Hole Difficulties for 1st time course in Simulation and Majors Not Played on Same Course
```{r}

#U.S. Open
hole_difficulties_per_tournament %>% 
  filter(tournament_name == "U.S. Open") %>% 
  group_by(tournament_name) %>% 
  summarise(across(
    .cols = c(easy:medium),
    .fns = mean
  )) %>% 
# The Open
  bind_rows(
    hole_difficulties_per_tournament %>% 
  filter(tournament_name == "The Open") %>% 
  group_by(tournament_name) %>% 
  summarise(across(
    .cols = c(easy:medium),
    .fns = mean
  ))
  ) %>% 
# PGA Championship
  bind_rows(
    hole_difficulties_per_tournament %>% 
  filter(tournament_name == "PGA Championship") %>% 
  group_by(tournament_name) %>% 
  summarise(across(
    .cols = c(easy:medium),
    .fns = mean
  ))
  ) %>% 
# Standard PGA Event
 bind_rows(
hole_difficulties_per_tournament %>% 
  filter(!tournament_name %in% c("U.S. Open", "The Open", "Masters Tournament", "PGA Championship") &
           !tournament_name %>% str_detect("World Golf Championship") &
           !tournament_name %>% str_detect("WGC")) %>% 
  mutate(tournament_name = "standard_pga_event") %>% 
  group_by(tournament_name) %>% 
  summarise(across(
    .cols = c(easy:medium),
    .fns = mean
  ))
) %>% 
  mutate(across(
    .cols = c(easy:medium),
    .fns = round
  )) %>% 
  mutate(total_holes = easy + medium + hard) %>% 
  mutate(medium = case_when(
    total_holes == 19 ~ medium - 1,
    total_holes == 17 ~ medium + 1,
    TRUE ~ medium)) %>% 
  mutate(total_holes = easy + medium + hard)
```


# Join Tournaments to Sim with Hole Difficulty Data
```{r}
tournaments_with_difficulty_to_sim <- 
  tournaments_to_sim %>%
  left_join(hole_difficulties_per_tournament,
            by = c("tournament_name", "course")) %>%
  mutate(
    easy = case_when(
      tournament_name == "U.S. Open" ~ 1,
      tournament_name == "The Open" ~ 2,
      tournament_name == "PGA Championship" ~ 2,
      TRUE ~ easy
    )
  ) %>%
  mutate(
    medium = case_when(
      tournament_name == "U.S. Open" ~ 5,
      tournament_name == "The Open" ~ 5,
      tournament_name == "PGA Championship" ~ 7,
      TRUE ~ medium
    )
  ) %>%
  mutate(
    hard = case_when(
      tournament_name == "U.S. Open" ~ 12,
      tournament_name == "The Open" ~ 11,
      tournament_name == "PGA Championship" ~ 9,
      TRUE ~ hard
    )
  ) %>% 
  mutate(easy = if_else(is.na(easy), 2, easy),
         medium = if_else(is.na(medium), 9, medium),
         hard = if_else(is.na(hard), 7, hard)) %>% 
  mutate(total_holes = 18)
```

# Read in Past Hole Category Data
```{r}
hole_category_values <- 
  hole_categories_tbl %>% 
  group_by(hole_category) %>% 
  summarise(min_adj_field_dk_avg = min(adj_field_dk_avg, na.rm = TRUE),
            max_adj_field_dk_avg = max(adj_field_dk_avg, na.rm = TRUE)) %>% 
  filter(hole_category == "medium") %>% 
  pivot_longer(-hole_category) %>% 
  pull(value)
```

# Pull tournament to sim
```{r}

tournament_ids <- 
  tournaments_to_sim %>% 
  pull(tournament_id)

tournament_dates <- 
  tournaments_to_sim %>% 
  pull(date)

get_tournament_players <- function(df, tid) {
  
  df %>%
    filter(tournament_id %in% c(tid)) %>%
    pull(player)
  
}

tournament_players_tbl <-
  map(tournament_ids, ~ get_tournament_players(dk_past_results, .x)) %>% 
  enframe(value = "players") %>% 
  bind_cols(tournament_id = tournament_ids, date = tournament_dates) %>% 
  unnest(players) %>% 
  left_join(select(tournaments_with_difficulty_to_sim, tournament_id, easy, medium, hard), by = "tournament_id") %>% 
  nest(-name)
  



```

# Run Simulations

# All 2019 season sims
```{r}
adj_dk_course_fit_sims_summarized <- 
  tournament_players_tbl %>%
  select(data) %>% 
  pmap(purrr::possibly(~ complete_simulation_framework(.x, cut_range = 70, six_week_weight = 1,
                                                      three_month_weight = 1, six_month_weight = 1), otherwise = NA))

adj_dk_course_fit_sims_tbl <- 
  adj_dk_course_fit_sims_summarized %>% 
  enframe(value = "sims") %>% 
  unnest(sims)

adj_dk_course_fit_sims_tbl %>%
  select(-name) %>% 
  mutate(sim_type = "adjusted_with_course_fit") %>% 
  write_csv("simulation_results/adjusted_with_course_fit_sims.csv")
```


```{r}
# Sims vs. Actual

adjusted_dk_course_fit_sims_with_actual_tbl <- 
  adj_dk_course_fit_sims_tbl %>%
  left_join(
    select(
      dk_past_results,
      player,
      tournament_id,
      final_position,
      dk_total_fp
    ),
    by = c("tournament_id",
      "player_name" = "player")
  )

write_csv(adjusted_dk_course_fit_sims_with_actual_tbl, "adjusted_dk_course_fit_sim_results.csv")

```

# Analyzing Results
```{r}

adjusted_dk_course_fit_sim_results <- read_csv("adjusted_dk_course_fit_sim_results.csv") %>% 
  drop_na() %>% 
  mutate(final_position = ifelse(is.na(final_position), 100, final_position)) %>% 
  distinct()


# Evaluating Top 20 Prob
top_20_bins <-  c(-Inf, 10, 20, 30, 40, 50, 60, 70, 80, Inf)
top_20_labels <-  c("0%-10%", "10%-20%", "20%-30%", "30%-40%", "40%-50%", "50%-60%", "60%-70%", "70%-80%", "Over 80%")

top_20_dk_tbl <- 
  adjusted_dk_course_fit_sim_results %>% 
  group_by(tournament_id) %>% 
  mutate(actual_dk_point_rk = min_rank(-dk_total_fp)) %>%
  ungroup() %>% 
  mutate(actual_top_20_dk_finish = ifelse(actual_dk_point_rk <= 20, 1, 0),
         top_20_prediction_range = cut(top20_dk, breaks = top_20_bins, labels = top_20_labels))

top_20_dk_tbl %>% 
  group_by(top_20_prediction_range) %>% 
  summarise(total_predicted = n(),
            top_20_dk_finishes = sum(actual_top_20_dk_finish)
            ) %>% 
  mutate(actual_top20_percentage = top_20_dk_finishes/total_predicted) %>% 
  ggplot(aes(top_20_prediction_range, actual_top20_percentage)) + 
  geom_point() +
  scale_y_continuous(breaks = seq(0, 1, .10), labels = scales::percent_format(accuracy = 1)) +
  labs(x = "Predicted",
       y = "Actual")
```

```{r}
# Evaluating Top 10 Prob
top_10_bins <-  top_5_bins <-  c(-Inf, 10,  20,  30, 40, 50, Inf)
top_10_labels <-  c("0%-10%", "10%-20%", "20%-30%", "30%-40%", "40%-50%", "Over 50%")

top_10_dk_tbl <- 
  adjusted_dk_course_fit_sim_results %>% 
  group_by(tournament_id) %>% 
  mutate(actual_dk_point_rk = min_rank(-dk_total_fp)) %>%
  ungroup() %>% 
  mutate(actual_top_10_dk_finish = ifelse(actual_dk_point_rk <= 10, 1, 0),
         top_10_prediction_range = cut(top10_dk, breaks = top_10_bins, labels = top_10_labels)) %>%
  select(top_10_prediction_range, actual_top_10_dk_finish)

top_10_dk_tbl %>% 
  group_by(top_10_prediction_range) %>% 
  summarise(total_predicted = n(),
            top_10_dk_finishes = sum(actual_top_10_dk_finish)
            ) %>% 
  mutate(actual_top_10_percentage = top_10_dk_finishes/total_predicted) %>% 
  ggplot(aes(top_10_prediction_range, actual_top_10_percentage)) + 
  geom_point() +
  scale_y_continuous(breaks = seq(0, .40, .10), labels = scales::percent_format(accuracy = 1)) +
  labs(x = "Predicted",
       y = "Actual")

```

```{r}

# Evaluating Top 5 Prob
top_5_bins <-  c(-Inf, 5, 10, 15, 20, 25, 30, Inf)
top_5_labels <-  c("0%-5%", "5%-10%", "10%-15%", "15%-20%", "20%-25%", "25%-30%", "Over 30%")

top_5_dk_tbl <- 
  adjusted_dk_course_fit_sim_results %>% 
  group_by(tournament_id) %>% 
  mutate(actual_dk_point_rk = min_rank(-dk_total_fp)) %>%
  ungroup() %>% 
  mutate(actual_top_5_dk_finish = ifelse(actual_dk_point_rk <= 5, 1, 0),
         top_5_prediction_range = cut(top5_dk, breaks = top_5_bins, labels = top_5_labels)) %>%
  select(top_5_prediction_range, actual_top_5_dk_finish)

top_5_dk_tbl %>% 
  group_by(top_5_prediction_range) %>% 
  summarise(total_predicted = n(),
            top_5_dk_finishes = sum(actual_top_5_dk_finish)
            ) %>% 
  mutate(actual_top_5_percentage = top_5_dk_finishes/total_predicted) %>% 
  ggplot(aes(top_5_prediction_range, actual_top_5_percentage)) + 
  geom_point() +
  scale_y_continuous(breaks = seq(0, .45, .05), labels = scales::percent_format(accuracy = 1)) +
  labs(x = "Predicted",
       y = "Actual")
```


# All 2019 season recent form weighted sims
```{r}
adj_dk_course_fit_weighted_sims_summarized <- 
  tournament_players_tbl %>%
  select(data) %>% 
  pmap(purrr::possibly(~ complete_simulation_framework(.x, three_month_weight = 1.10, six_month_weight = 1.05), otherwise = NA))

adj_dk_course_fit_weighted_sims_tbl <- 
  adj_dk_course_fit_weighted_sims_summarized %>% 
  enframe(value = "sims") %>% 
  unnest(sims)
```

```{r}
# Sims vs. Actual

adjusted_dk_course_fit_weighted_sims_with_actual_tbl <- 
  adj_dk_course_fit_weighted_sims_tbl %>%
  left_join(
    select(
      dk_past_results,
      player,
      tournament_id,
      final_position,
      dk_total_fp
    ),
    by = c("tournament_id",
      "player_name" = "player")
  )

write_csv(adjusted_dk_course_fit_weighted_sims_with_actual_tbl, "adjusted_dk_course_fit_weighted_sim_results.csv")

```

# Analyzing Results
```{r}

adjusted_dk_course_fit_weighted_sims_with_actual_tbl <- 
  read_csv("adjusted_dk_course_fit_weighted_sim_results.csv") %>% 
  select(-name) %>% 
  mutate(final_position = ifelse(is.na(final_position), 100, final_position)) %>% 
  distinct() %>% 
  drop_na()


# Evaluating Top 20 Prob
top_20_bins <-  c(-Inf, 10, 20, 30, 40, 50, 60, 70, Inf)
top_20_labels <-  c("0%-10%", "10%-20%", "20%-30%", "30%-40%", "40%-50%", "50%-60%", "60%-70%", "Over 70%")

top_20_dk_tbl <- 
  adjusted_dk_course_fit_weighted_sims_with_actual_tbl %>% 
  group_by(tournament_id) %>% 
  mutate(actual_dk_point_rk = min_rank(-dk_total_fp)) %>%
  ungroup() %>% 
  mutate(actual_top_20_dk_finish = ifelse(actual_dk_point_rk <= 20, 1, 0),
         top_20_prediction_range = cut(top20_dk, breaks = top_20_bins, labels = top_20_labels))

top_20_dk_tbl %>% 
  group_by(top_20_prediction_range) %>% 
  summarise(total_predicted = n(),
            top_20_dk_finishes = sum(actual_top_20_dk_finish)
            ) %>% 
  mutate(actual_top20_percentage = top_20_dk_finishes/total_predicted) %>% 
  ggplot(aes(top_20_prediction_range, actual_top20_percentage)) + 
  geom_point() +
  scale_y_continuous(breaks = seq(0, 1, .10), labels = scales::percent_format(accuracy = 1)) +
  labs(x = "Predicted",
       y = "Actual")
```

```{r}
# Evaluating Top 10 Prob
top_10_bins <-  c(-Inf, 10, 20, 30, 40, 50, Inf)
top_10_labels <-  c("0%-10%", "10%-20%", "20%-30%", "30%-40%", "40%-50%", "Over 50%")

top_10_dk_tbl <- 
  adjusted_dk_course_fit_weighted_sims_with_actual_tbl %>% 
  group_by(tournament_id) %>% 
  mutate(actual_dk_point_rk = min_rank(-dk_total_fp)) %>%
  ungroup() %>% 
  mutate(actual_top_10_dk_finish = ifelse(actual_dk_point_rk <= 10, 1, 0),
         top_10_prediction_range = cut(top10_dk, breaks = top_10_bins, labels = top_10_labels))

top_10_dk_tbl %>% 
  group_by(top_10_prediction_range) %>% 
  summarise(total_predicted = n(),
            top_10_dk_finishes = sum(actual_top_10_dk_finish)
            ) %>% 
  mutate(actual_top10_percentage = top_10_dk_finishes/total_predicted) %>% 
  ggplot(aes(top_10_prediction_range, actual_top10_percentage)) + 
  geom_point() +
  scale_y_continuous(breaks = seq(0, 1, .10), labels = scales::percent_format(accuracy = 1)) +
  labs(x = "Predicted",
       y = "Actual")
```

